%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2016.
%
%  Author: Sean Zachary Roberson
%	 Version 3.17.01
%  Last updated 1/10/2017
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.


\indent All praise be to Allah, the most gracious and the most merciful.

I feel most fortunate and blessed to have Dr. Robert Nevels as my advisor who  made himself available to me, gave me excellent technical advice, provided me freedom to pursue personal research and academic interests and above all taught me to become a better human being. I feel privileged to learn from Dr. Krzysztof Michalski who helped me immensely to analyze layered media through his papers and answering my questions. I would like to thank Dr. Chin Su, who introduced me to plasmonics through the nanophotonics. Being a Pakistani, it has been an honor to work and collaborate with Dr. Suhail Zubairy who suggested on investigating imaging aspects through the surface wave structure discussed in this dissertation.

I would like to thank my colleague and friend Jongchul Shin, with whom I shared my office, for all the philosophical discussions and in particular making my stay pleasurable. I am grateful to Muhammad Al-Khalidi, for providing the motivation to get things done in a timely manner. My former colleagues, Sean Goldberger, Justin Erdle, Sungyun Jun for helping me settle in the Electromagnetics and Microwave lab (EML). I must also thank Feyza Berber for clarifying various practical aspects of semiconductor fabrication specific to this work.

I am indebted to all the great teachers starting from kindergarten to my time at Texas A\&M University. I especially thank my high-school chemistry teacher Rana Muhammad Akram whose mentoring ensured that I remain focused in achieving educational goals. I owe a lot to the Islamic community in College Station that was always there for moral and spiritual support. A special thanks goes to the Khan family for making me part of the family and taking care of my family. My friends Sabeeh Ahmed, Sameer Farooqi, Umer Misgar, Bilal Wajid, Shayan Arshed and Yusuf Dogan for making my time in College Station a fond memory. My friends back in Pakistan; Hammad Akram, Ali Yazdani, Salim Butt and Ahmad Saad who stayed in touch and frequently inquired about my progress and well-being.

I am grateful to my mother Yasmeen Tahir and my father, Tahir Abbas for their love, support, understanding and prayers; my maternal aunt Nasreen Safdar for the  affection towards me during my time in Lahore; my brother Saad and sister Rabea for all the childhood memories that have shaped me who I am today. Finally, I would like to thank my dear wife, Tooba Ather who patiently endured so much during our time in College Station, from taking care of our daughter Ayesha all by herself, to letting me focus on this work. Without her, this dissertation would not have become a reality.

\pagebreak{}
